\begin{thebibliography}{} 

\bibitem[Bakshi \& Srinivasan(2025)]{bakshi_quantum_2025}
Bakshi, K., \& Srinivasan, K. (2025). Quantum inspired qubit qutrit neural networks for real time financial forecasting. \textit{Scientific Reports}, 15(1), 28711.

\bibitem[Eisert et al.(1999)]{eisert_quantum_1999}
Eisert, J., Wilkens, M., \& Lewenstein, M. (1999). Quantum games and quantum strategies. \textit{Physical Review Letters}, 83(15), 3077.

\bibitem[El-Nabulsi \& Anukool(2025)]{el-nabulsi_qualitative_2025}
El-Nabulsi, R. A., \& Anukool, W. (2025). Qualitative financial modelling in fractal dimensions. \textit{Financial Innovation}, 11(1), 42.

\bibitem[Layden et al.(2022)]{layden_quantum-enhanced_2022}
Layden, D., Mazzola, G., Mishmash, R. V., Motta, M., Wocjan, P., Kim, J.-S., \& Sheldon, S. (2022). Quantum-enhanced Markov chain Monte Carlo. \textit{arXiv preprint arXiv:2203.12497}.

\bibitem[Li \& Papanicolaou(2022)]{li_statistical_2022}
Li, T. N., \& Papanicolaou, A. (2022). Statistical Arbitrage for Multiple Co-integrated Stocks. \textit{Applied Mathematics \& Optimization}, 86(1), 12.

\bibitem[Lowe(2024)]{lowe_linking_2024}
Lowe, A. (2024). Linking quantum discord with Bayesian game theory. \textit{arXiv preprint arXiv:2407.21730}.

\bibitem[Marinatto \& Weber(2000)]{marinatto_quantum_2000}
Marinatto, L., \& Weber, T. (2000). A quantum approach to static games of complete information. \textit{Physics Letters A}, 272(5-6), 291--303.

\bibitem[Meyer(1999)]{meyer_quantum_1999}
Meyer, D. A. (1999). Quantum Strategies. \textit{Physical Review Letters}, 82(5), 1052--1055.

\bibitem[Moreira et al.(2020)]{moreira_quantum-like_2020}
Moreira, C., Tiwari, P., Pandey, H. M., Bruza, P., \& Wichert, A. (2020). Quantum-like influence diagrams for decision-making. \textit{Neural Networks}, 132, 190--210.

\bibitem[Samadi et al.(2017)]{samadi_quantum_2017}
Samadi, A. H., Montakhab, A., Marzban, H., \& Owjimehr, S. (2017). Quantum Barro–Gordon Game in Monetary Economics. \textit{arXiv preprint arXiv:1708.05689}.

\bibitem[Schwert(2003)]{schwert_chapter_2003}
Schwert, G. W. (2003). Anomalies and market efficiency. In \textit{Handbook of the Economics of Finance} (Vol. 1, pp. 939--974). Elsevier.

\bibitem[Sinaga et al.(2023)]{sinaga_important_2023}
Sinaga, T. J. H., Anwar, K., Amalia, N., Sunnardianto, G. K., \& Budiman, G. (2023). Important Quantum Gates for Quantum Algorithms of Travelling Salesman Problem. \textit{2023 International Conference on Artificial Intelligence, Blockchain, Cloud Computing, and Data Analytics (ICoABCD)}, 146--151.

\bibitem[Tversky \& Shafir(1992)]{tversky_disjunction_1992}
Tversky, A., \& Shafir, E. (1992). The Disjunction Effect in Choice under Uncertainty. \textit{Psychological Science}, 3(5), 305--310.

\bibitem[Wang et al.(2018)]{wang_deep_2018}
Wang, H., Chen, H., Sudjianto, A., Liu, R., \& Shen, Q. (2018). Deep Learning-Based BSDE Solver for Libor Market Model with Application to Bermudan Swaption Pricing and Hedging. \textit{arXiv preprint arXiv:1807.06622}.

\end{thebibliography}